Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2017-07-27 writeup/conStruct.tex
merged graham's edits

\title{Inferring Continuous and Discrete Population Genetic Structure Across Space}
\date{\vspace{-5ex}}
\author{
Gideon S. Bradburd$^{1,a}$, 
Peter L. Ralph$^{2,b}$, 
Graham M. Coop$^{3,c}$}

@@

\textsuperscript{2}
Institute of Ecology and Evolution,
Department of Mathematics,
University of Oregon, Eugene, OR 97403

\textsuperscript{3}
Center for Population Biology,
Department of Evolution and Ecology, 
University of California, Davis, CA 95616

\textsuperscript{a}bradburd@msu.edu; 
\textsuperscript{b}plr@uoregon.edu;
\textsuperscript{c}gmcoop@ucdavis.edu\\\\\

@@

There have been many methods proposed to characterize populations,
including generating population phylogenies \citep{CavalliSforza1975, treemix},
$k$-means clustering analyses performed on dimensionality-reduction approaches \citep{}, 
such as principal components analysis \citep{menozzi1978synthetic,novembre_interpreting_2008, price2006eigenstrat},
and model-based clustering approaches \citep[e.g.][]{STRUCTURE, falush2003, hubisz2009,ADMIXTURE, FINESTRUCTURE, huelsenbeck2007inference, Corander2003,TESS}, among others.
Here, we will focus on model-based clustering, the most widely used class of approaches.
These methods each perform best under different specific demographic histories of samples being analyzed,
but all can give misleading results when applied to data that show a continuous pattern of isolation by distance \citep{Wright 1938, 1940, Wright1943}.

A pattern of isolation by distance (IBD) arises when migration in a population is spatially limited \citep{Slatkin1985},
and has been modeled in both spatially continuous frameworks \citep{Wright1943,Malecot1948}, 
in which an individual's parents are found within some radius of that individual's location,
and discrete, ``stepping-stone'' frameworks \citep{Kimura1953},
in which migration occurs only between neighboring demes.
Given the generality of the circumstances that generate a pattern of isolation by distance, 
it is unsurprising that IBD is ubiquitous in nature \citep{meirmans2012,Sexton_etal_2014}.

@@

Existing model-based clustering approaches can only describe continuous patterns of variation using
discrete clusters, 
and so tend to erroneously describe continuously distributed variation with multiple clusters that 
show spatially autocorrelated cluster membership \citep{Frantz2009,Meirmans2012}.
In analyses of empirical datasets, which often are characterized by IBD,
model-based clustering approaches will therefore tend to overestimate the number of discrete clusters present,
with downstream implications for interpretation of results.
For example, conservation resources might be spread too thinly over areas 
that are spuriously assumed to be discrete management units.
In studies of locally adaptive loci, or of the genetics of disease,
discrete populations may be modeled in separately,
reducing the global power to detect the genomic basis of complex phenotypes.

What is desired, then, is a model-based clustering method that incorporates a spatial element.
and specifically one that uses a model of isolation by distance as a biologically sensible null hypothesis 
for the process structuring observed genetic variation.
With an explicit spatial null, discrete population structure need only be invoked when genetic differentiation 
in the data is above and beyond that expected given some estimated background rate at which divergence 
increases with geographic separation.

In this paper, we present a statistical method for simultaneously 
modeling continuous and discrete patterns of population structure.
We model genetic variation in genotyped individuals as 
partitioned within or admixed across a user-specified number of discrete clusters,
within each of which relatedness decays as a parametric function of the distance between samples.
We also implement a cross-validation approach for comparing and selecting models across different numbers of clusters,
and we demonstrate the utility of our approach using both simulated and empirical data.
The implementation of this method, \texttt{conStruct}, is available as an R package at \href{https://github.com/gbradburd/conStruct}{https://github.com/gbradburd/conStruct}.

\section*{Methods}
\paragraph{Data}
The statistical framework of our approach is conceptually similar to \cite{Wasser2004} and \cite{BEDASSLE}, and \cite{spacemix}.
The genetic data modeled consist of allele frequencies $F$ at $L$ unlinked, bi-allelic single nucleotide polymorphisms (SNPs) genotyped across $N$ samples.
The sample frequency at locus $\ell$ in sample $n$, $f_{n,\ell}$, is calculated by first arbitrarily choosing an allele segregating 
at locus $\ell$ to count, 
then dividing the total number of observations of that counted allele by the total number of chromosomes genotyped at that locus
in sample $n$.
We then calculate the sample covariance in allele frequencies, $\widehat{\Omega}$, as

\begin{equation}
\widehat{\Omega} = \frac{1}{L}  FF^T
\label{sample_covariance}
\end{equation}

\paragraph{Continuous and discrete differentiation}
We wish to describe the observed patterns of genetic variation as a combination of 
discrete population clusters,
within which genetic variation is continuously distributed, 
and between which sampled individuals or populations can be admixed.
Each of these discrete clusters is modeled as a spatial process
in which migration between neighboring demes acts 
to homogenize allele frequency changes that arise locally due to drift;
this interplay between drift and migration 
results in a continuous pattern of isolation by distance within each cluster.
Multiple population cluster processes can co-occur in space, 
leading to discrete jumps in allele frequencies across many loci over small geographic distances,
and the genotyped samples can be admixed between different clusters.

The continuous decay of allele frequency covariance with geographic distance 
within a cluster is described using a simple and flexible powered exponential function;
the within-cluster covariance between samples $i$ and $j$ is given by:

@@

where $G_{i,j}$ is the covariance function between samples $i$ and $j$ within a cluster,
and the superscript $(k)$ denotes that this function is specific to the $k$th cluster.
The quantity $D_{i,j}$ is the observed geographic distance between samples $i$ and $j$,
the $\alpha$ parameters control the shape of the decay of covariance with distance,
and $\mu$ is a parameter that describes the amount of shared drift within a cluster.
The shared drift parameter $\mu^{(k)}$ can be interpreted as the branch length connecting 
the $k$th population to the population ancestral to all modeled clusters.

Genotyped samples can be admixed between these different clusters. 
The admixture proportion of the $i$th sample in the $k$th cluster, $w^{(k)}_i$,
gives the probability that an allele in sample $i$ was derived from cluster $k$;
each sample's admixture proportions across all clusters must sum to one.

We can then describe the covariance between samples $i$ and $j$ across all clusters, $\Omega_{i,j}$,
by summing their within-cluster spatial covariances ($G_{i,j}^{(k)}$ in cluster $k$) across all $K$ clusters
and weighting by the product of those samples' admixture proportions in each cluster.

\begin{equation}
\Omega_{i,j} = \gamma + \sum\limits_K w^{(k)}_i w^{(k)}_j G^{(k)}_{i,j} + \delta_{i,j}\eta_i
\label{cross_cluster_covariance}
\end{equation}

In addition to the admixture-weighted sum of the within-cluster spatial covariances,
this function contains two terms, $\gamma$ and $\delta_{i,j}\eta_i$.
The first, $\gamma$, describes the global covariance between all samples, 
and arises because all samples share an ancestral mean allele frequency at each locus.
In the second term, $\delta_{i,j}$ is an indicator variable that takes a value of 1 when $i$ equals $j$ and 0 otherwise. 
and $\eta_i$ gives the variance specific to sample $i$, 
This term on the diagonal of the parametric covariance matrix 
is meant to capture processes shaping variance within the sampled deme, 
such as inbreeding.

\paragraph{Likelihood and inference}
If we assume that the  allele frequencies $\widehat{F}$ are independent and multivariate normally distributed, 
their sample covariance $\widehat{\Omega}$ 
will be Wishart distributed with degrees of freedom equal to $L$, 
the number of loci genotyped.
Linkage disequilibrium (LD) between loci will decrease the effective number of degrees of freedom, 
which we discuss further below.
The likelihood of the sample standardized allele frequency covariance is therefore given by
\begin{equation}
P(\widehat{\Omega} \; | \; \Omega) = \mathcal{W} \left( L\widehat{\Omega} \; | \; \Omega,L\right)
\end{equation}

We estimate the values of the parameters of the model using a Bayesian approach.
Acknowledging the dependence of the parametric covariance matrix $\Omega$ on its constituent parameters
$w,\alpha,\mu,\eta,\gamma$ and on observed quantiy $D$ with the notation $\Omega(w,\alpha,\mu,\eta,\gamma,D)$,
we denote the posterior probability of the parameters as:

@@

The priors, $P(w),P(\alpha),P(\mu),P(\eta),P(\gamma)$, are detailed in the Appendix,
and the constant of proportionality is the normalization constant.
We use a Hamiltonian Monte Carlo sampling algorithm implemented in the statistical language STAN
\citep{stan, NUTS, stan_lib, rstan} to estimate the posterior distribution on the parameters.
We also present an R package \citep{R} called \texttt{conStruct} that functions as a wrapper 
around this inference machinery.

@@

We ran \texttt{conStruct} analyses on each of these simulated datasets, 
specifying both a spatial and nonspatial model for $K = $ 1 through 7, 
then used cross-validation to compare the predictive performance of the models.
In Fig \ref{simK1_nsp_pies}, we show the results of the nonspatial model 
run with between 1 and 7 clusters, applied to the dataset simulated under $K=1$,
and in Fig \ref{xvals} we show the results of the cross-validation analysis for each of the three simulated datasets.
The admixture pie plots for the spatial and nonspatial models run on the datasets simulated under $K=2$ and $K=3$
are shown in Figs \ref{simK1_sp_pies}-\ref{simK3_sp_pies}.

A number of results are immediately clear from these tests with simulated data.
First, across all values of K and for all simulations, 
the spatial model is preferred over the nonspatial model
(this is not surprising, as the data were simulated under a spatial model).
Second, the predictive accuracy of the nonspatial model increases with the number of clusters in the model, 
as it describes continuous, spatial patterns of relatedness between demes within the same cluster 
with gradients of admixture across more and more discrete clusters.
This behavior of the nonspatial model is highlighted in the analyses of data simulated under $K=1$ (Fig \ref{simK1_nsp_pies}):
as $K$ in the model increases, 
the sampled area is increasingly divvied up between clusters 
with ``centers of mass" in the $K$ geographical extremes of the simulated space.
At $K=2$, the clusters are centered in opposite corners on the map; 
at $K=3$, in the lower two corners and the top half; 
at $K=4$, all four corners, and so on.

@@

@@

\begin{figure}
	\centering
		\subcaptionbox{$K=2$\label{simK1_nsp_pies:K2}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K2.pdf}}
		\subcaptionbox{$K=3$\label{simK1_nsp_pies:K3}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K3.pdf}}
		\subcaptionbox{$K=4$\label{simK1_nsp_pies:K4}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K4.pdf}}
		\subcaptionbox{$K=5$\label{simK1_nsp_pies:K5}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K5.pdf}}
		\subcaptionbox{$K=6$\label{simK1_nsp_pies:K6}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K6.pdf}}
		\subcaptionbox{$K=7$\label{simK1_nsp_pies:K7}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K7.pdf}}
	\caption{
	Map of admixture proportions estimated using a nonspatial model for $K=2$ through 7.
	The data were simulated using a single cluster with nearest-neighbor symmetric migration between demes.
    }\label{simK1_nsp_pies}
\end{figure}

@@

\newpage
\begin{figure}
	\centering
		\subcaptionbox{$K=2$\label{simK1_sp_pies:K2}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K2.pdf}}
		\subcaptionbox{$K=3$\label{simK1_sp_pies:K3}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K3.pdf}}
		\subcaptionbox{$K=4$\label{simK1_sp_pies:K4}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K4.pdf}}
		\subcaptionbox{$K=5$\label{simK1_sp_pies:K5}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K5.pdf}}
		\subcaptionbox{$K=6$\label{simK1_sp_pies:K6}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K6.pdf}}
		\subcaptionbox{$K=7$\label{simK1_sp_pies:K7}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K7.pdf}}
	\caption{
	Map of admixture proportions estimated using a spatial model for $K=2$ through 7.
	The data were simulated using 1 cluster with nearest-neighbor symmetric migration between demes.
    }\label{simK1_sp_pies}
\end{figure}

>>>>

\title{Inferring Continuous and Discrete Population Genetic Structure Across Space}
\date{\vspace{-5ex}}
\author{
Gideon S. Bradburd$^{1,a}$, 
Graham M. Coop$^{2,b}$,
Peter L. Ralph$^{3,c}$}

@@

\textsuperscript{2}
Center for Population Biology,
Department of Evolution and Ecology, 
University of California, Davis, CA 95616

\textsuperscript{3}
Institute of Ecology and Evolution,
Department of Mathematics,
University of Oregon, Eugene, OR 97403

\textsuperscript{a}bradburd@msu.edu; 
\textsuperscript{c}gmcoop@ucdavis.edu;
\textsuperscript{b}plr@uoregon.edu\\\\\

@@

There have been many methods proposed to characterize populations,
including generating population phylogenies \citep{CavalliSforza1975, treemix},
$k$-means clustering analyses performed on dimensionality-reduction approaches \citep{}, 
such as principal components analysis \citep{menozzi1978synthetic,novembre_interpreting_2008, price2006eigenstrat},
and model-based clustering approaches \citep[e.g.][]{STRUCTURE, falush2003, hubisz2009,ADMIXTURE, FINESTRUCTURE, huelsenbeck2007inference, Corander2003,TESS}, among others.
Here, we will focus on model-based clustering, the most widely used class of approaches for population delineation.
These methods each perform best under different specific demographic histories of samples being analyzed,
but all can give misleading results when applied to data that show a continuous pattern of isolation by distance \citep{Wright 1938, 1940, Wright1943}.

A pattern of isolation by distance (IBD) arises when migration in a population is spatially limited \citep{Slatkin1985},
and has been modeled in both spatially continuous frameworks \citep{Wright1943,Malecot1948}, 
in which an individual's parents are found within some radius of that individual's location,
and discrete, ``stepping-stone'' frameworks \citep{Kimura1953},
in which migration occurs only between neighboring demes.
Given the generality of the circumstances that generate a pattern of isolation by distance, 
it is unsurprising that IBD is found everywhere in nature \citep{meirmans2012,Sexton_etal_2014}.

@@

Existing model-based clustering approaches can only describe continuous patterns of variation using
discrete clusters, 
and so tend to erroneously describe continuously distributed variation with multiple clusters that 
show spatially autocorrelated cluster membership \citep{Frantz2009,Meirmans2012}.
In analyses of empirical datasets, which often are characterized by IBD,
model-based clustering approaches will therefore tend to overestimate the number of discrete clusters present,
with downstream implications for interpretation of results.
For example, conservation resources might be spread too thinly over areas 
that are spuriously assumed to be discrete management units.
Or, in studies of locally adaptive loci, or of the genetics of disease,
discrete populations may be modeled in separately,
reducing the global power to detect the genomic basis of complex phenotypes.

What is desired, then, is a model-based clustering method that incorporates a spatial element,
and specifically one that uses a model of isolation by distance as a biologically sensible null hypothesis 
for the process structuring observed genetic variation.
With an explicit spatial null, discrete population structure need only be invoked when genetic differentiation 
in the data is above and beyond that expected given some estimated background rate at which divergence 
increases with geographic separation.

In this paper, we present a statistical method for simultaneously 
modeling continuous and discrete patterns of population structure.
We model genetic variation in genotyped individuals as 
partitioned within or admixed across a specified number of discrete clusters,
within each of which relatedness decays as a parametric function of the distance between samples.
We also implement a cross-validation approach for comparing and selecting models across different numbers of clusters,
and we demonstrate the utility of our approach using both simulated and empirical data.
The implementation of this method, \texttt{conStruct}, is available as an R package at 
\href{https://github.com/gbradburd/conStruct}{https://github.com/gbradburd/conStruct}.

\section*{Methods}
\paragraph{Data}
The statistical framework of our approach is conceptually similar to \cite{Wasser2004} and \cite{BEDASSLE}, and \cite{spacemix}.
The genetic data modeled consist of allele frequencies $F$ at $L$ unlinked, bi-allelic single nucleotide polymorphisms (SNPs) genotyped across $N$ samples.
The sample frequency at locus $\ell$ in sample $n$, $f_{n,\ell}$, is calculated by first arbitrarily choosing an allele segregating 
at locus $\ell$ to count, 
then dividing the total number of observations of that counted allele by the total number of chromosomes genotyped at that locus
in sample $n$.
We then calculate the sample covariance in allele frequencies, $\widehat{\Omega}_{i,j}$ between samples $i$ and $j$.
However, for the diagonal of this sample covariance (the variances within each sample),
we wish to describe the mean of the variance in allele frequencies between haplotypes in a sample, 
rather than the variance of the mean frequencies across haplotypes in a sample.
Therefore, we calculate our sample covariance as follows:

\begin{equation}
\widehat{\Omega}_{i,j} = 
	\begin{cases}
		\frac{1}{L}
		\sum\limits_{\ell=1}^{L}{\left[ 	\left(f_{i,\ell} - \bar{f}_{\ell} \right)
		 	\left(f_{j,\ell} - \bar{f}_{\ell} \right)\right]
			} & \text{for } i \neq j \\
		\text{Var}_L\left( \text{B}(1,f_{i,\ell})	\right) & \text{for } i = j \\
	\end{cases}
\label{sample_covariance}
\end{equation}
\gb{ideas for how to describe what I'm doing on the diagonal in actual math notation?}

\paragraph{Continuous and discrete differentiation}
We wish to describe the observed patterns of genetic variation as a combination of 
discrete population clusters,
within which genetic variation is continuously distributed, 
and between which sampled individuals or populations can be admixed.
Each of these discrete clusters is modeled as a spatial process in which
allele frequencies covary between geographically close locations,
but this covariance is allowed to decay with geographic distance.
This pattern of spatial decay reflects how migration between neighboring demes  
homogenizes allele frequency changes that arise locally due to drift, 
but is less effective at homogenizing between geographic distant demes,
resulting in a continuous pattern of isolation by distance within each cluster.
Multiple population cluster processes can co-occur in space, 
leading to discrete jumps in allele frequencies across many loci over small geographic distances,
and the genotyped samples can be admixed between different clusters.

To model the continuous decay of allele frequency covariance with geographic distance within a cluster, 
we use a flexible powered-exponential function;
the within-cluster covariance between samples $i$ and $j$ is given by:

@@

where $G_{i,j}$ is the covariance function between samples $i$ and $j$ within a cluster,
and the superscript $(k)$ denotes that this function is specific to the $k$th cluster.
The quantity $D_{i,j}$ is the observed geographic distance between samples $i$ and $j$,
the $\alpha^{(k)}$ parameters control the shape of the decay of covariance with distance in the cluster,
and $\mu$ is a parameter that describes the background allele frequency covariance within the cluster. 
If two samples draw 100\% of their ancestry from cluster $k$ then, 
if they are geographically very close ($D_{i,j}=0$) 
they will have allele frequency covariance $\alpha^{(k)}_0 +  \mu^{(k)}$.
If the geographic distance between them is very large, 
their covariance will decay to the background level $\mu^{(k)}$ within the cluster.
The shared drift parameter $\mu^{(k)}$ can be interpreted as the branch length 
connecting the $k$th population to the population ancestral to all modeled
clusters \gc{(see XXX)}. \gb{is ``XXX" TreeMix? or one of the $f$stat papers?  or is it a figure?}

Genotyped samples can draw their ancestry from multiple different clusters,
representing these samples being admixed between the clusters.
The admixture proportion of the $i$th sample in the $k$th cluster, $w^{(k)}_i$,
gives the probability that an allele in sample $i$ was derived from
cluster $k$ ($\sum_K w^{(k)}_i =1$).

We can then describe the covariance between samples $i$ and $j$ across all clusters, $\Omega_{i,j}$,
by summing their within-cluster spatial covariances ($G_{i,j}^{(k)}$ in cluster $k$) across all $K$ clusters
and weighting by the product of those samples' admixture proportions in each cluster
\begin{equation}
\Omega_{i,j} = \gamma + \sum\limits_K w^{(k)}_i w^{(k)}_j
G^{(k)}_{i,j} + \delta_{i,j}\eta_i .
\label{cross_cluster_covariance}
\end{equation}

In addition to the admixture-weighted sum of the within-cluster spatial covariances,
this function contains two terms, $\gamma$ and $\delta_{i,j}\eta_i$.
The first, $\gamma$, describes the global covariance between all samples, 
and arises because all samples share an ancestral mean allele frequency at each locus,
which generates a base-line covariance.
In the second term, $\delta_{i,j}$ is an indicator variable that takes a value of 1 when $i$ equals $j$ and 0 otherwise. 
and $\eta_i$ gives the variance specific to sample $i$, 
This term on the diagonal of the parametric covariance matrix captures processes shaping variance within the sampled deme, 
such as inbreeding and the sampling process.

\paragraph{Likelihood and inference}
We assume that the allele frequencies at each locus ($\widehat{F}_{\ell}$) 
are independent among loci and multivariate normally distributed across populations, 
so that their sample covariance $\widehat{\Omega}$ 
is  Wishart distributed with degrees of freedom equal to $L$, 
the number of loci genotyped.
Linkage disequilibrium (LD) between loci will decrease the effective number of degrees of freedom, 
which we discuss further below.
The likelihood of the sample standardized allele frequency covariance is therefore given by
\begin{equation}
P(\widehat{\Omega} \; | \; \Omega) = \mathcal{W} \left( L\widehat{\Omega} \; | \; \Omega,L\right)
\end{equation}

We estimate the values of the parameters of the model using a Bayesian approach.
Acknowledging the dependence of the parametric covariance matrix $\Omega$ on its constituent parameters
$w,\alpha,\mu,\eta,\gamma$ and on observed quantity $D$ 
with the notation $\Omega(w,\alpha,\mu,\eta,\gamma,D)$,
we denote the posterior probability of the parameters as:

@@

The priors, $P(w),P(\alpha),P(\mu),P(\eta),P(\gamma)$, are detailed in Table \ref{tab:param_prior_tab},
and the constant of proportionality is the normalization constant.
We use a Hamiltonian Monte Carlo sampling algorithm implemented in the statistical language STAN
\citep{stan, NUTS, stan_lib, rstan} to estimate the posterior distribution on the parameters.
We also present an R package \citep{R} called \texttt{conStruct} that functions as a wrapper 
around this inference machinery.

\gc{
\paragraph{Relationship of this model to non-spatial structure models}

}

\gc{ 
\paragraph{Choice of cluster number and cross-validation}

}

@@

We ran \texttt{conStruct} analyses on each of these simulated datasets, 
specifying both a spatial and nonspatial model for $K = $ 1 through 7, 
then used cross-validation to compare the predictive performance of the models.
In Fig \ref{simK1_pies}, we show the results of the nonspatial model 
run with between 1 and 7 clusters, applied to the dataset simulated under $K=1$,
and in Fig \ref{xvals} we show the results of the cross-validation analysis for each of the three simulated datasets.
The admixture pie plots for the spatial and nonspatial models run on the datasets simulated under $K=2$ and $K=3$
are shown in Figs \ref{simK1_nsp_pies}-\ref{simK3_sp_pies}.

A number of results are immediately clear from these tests with simulated data.
First, across all values of K and for all simulations, 
the spatial model is preferred over the nonspatial model
(this is not surprising, as the data were simulated under a spatial model).
Second, the predictive accuracy of the nonspatial model increases with the number of clusters in the model, 
as it describes continuous, spatial patterns of relatedness between demes within the same cluster 
with gradients of admixture across more and more discrete clusters.
This behavior of the nonspatial model is highlighted in the analyses of data simulated under $K=1$ (Fig \ref{simK1_pies} and \ref{simK1_nsp_pies}):
as $K$ in the model increases, 
the sampled area is increasingly divvied up between clusters 
with ``centers of mass" in the $K$ geographical extremes of the simulated space.
At $K=2$, the clusters are centered in opposite corners on the map; 
at $K=3$, in the lower two corners and the top half; 
at $K=4$, all four corners, and so on.

@@

\begin{figure}
	\centering
		\subcaptionbox{$K=2$\label{simK1_nsp_pies:K2}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K2.pdf}}
		\subcaptionbox{$K=3$\label{simK1_nsp_pies:K3}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K3.pdf}}
		\subcaptionbox{$K=4$\label{simK1_nsp_pies:K4}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K4.pdf}}
		\subcaptionbox{$K=2$\label{simK1_sp_pies:K2}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K5.pdf}}
		\subcaptionbox{$K=3$\label{simK1_sp_pies:K3}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K6.pdf}}
		\subcaptionbox{$K=4$\label{simK1_sp_pies:K4}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K7.pdf}}
	\caption{
	Map of admixture proportions estimated using the nonspatial model for $K=2$ through 4 (top row)
	and also the spatial model for $K=2$ through 4 (bottom row).
	The data were simulated using a single cluster with nearest-neighbor symmetric migration between demes.
    }\label{simK1_pies}
\end{figure}

@@

@@

\newpage
\begin{figure}
	\centering
		\subcaptionbox{$K=2$\label{simK1_nsp_pies:K2}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K2.pdf}}
		\subcaptionbox{$K=3$\label{simK1_nsp_pies:K3}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K3.pdf}}
		\subcaptionbox{$K=4$\label{simK1_nsp_pies:K4}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K4.pdf}}
		\subcaptionbox{$K=5$\label{simK1_nsp_pies:K5}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K5.pdf}}
		\subcaptionbox{$K=6$\label{simK1_nsp_pies:K6}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K6.pdf}}
		\subcaptionbox{$K=7$\label{simK1_nsp_pies:K7}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_nsp_pies_K7.pdf}}
	\caption{
	Map of admixture proportions estimated using a nonspatial model for $K=2$ through 7.
	The data were simulated using a single cluster with nearest-neighbor symmetric migration between demes.
    }\label{simK1_nsp_pies}
\end{figure}

\begin{figure}
	\centering
		\subcaptionbox{$K=2$\label{simK1_sp_pies:K2}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K2.pdf}}
		\subcaptionbox{$K=3$\label{simK1_sp_pies:K3}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K3.pdf}}
		\subcaptionbox{$K=4$\label{simK1_sp_pies:K4}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K4.pdf}}
		\subcaptionbox{$K=5$\label{simK1_sp_pies:K5}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K5.pdf}}
		\subcaptionbox{$K=6$\label{simK1_sp_pies:K6}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K6.pdf}}
		\subcaptionbox{$K=7$\label{simK1_sp_pies:K7}}
			{\includegraphics[width=1.8in,height=1.8in]{figs/sims/simK1_sp_pies_K7.pdf}}
	\caption{
	Map of admixture proportions estimated using a spatial model for $K=2$ through 7.
	The data were simulated using 1 cluster with nearest-neighbor symmetric migration between demes.
    }\label{simK1_sp_pies}
\end{figure}
